\thetitle: Technical Report

### 2023-04-05 frontmatters.tex
Adding List of Figures.
Adding list of figures.
List of Figures now working. But might fail sometime. Just be aware.
Fix TOC
Adding List of Abbrev.
Add backmatters
Adding Front Page
Update Acknowledgement

% Title Page
\pagenumbering{roman}
\vspace*{\fill}
\begin{center}
  \textsc{\Huge \thetitle}
\end{center}

@@

We thank Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, and Zhixuan Yang
for valuable discussions and feedback.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the authors and do not necessarily
reflect the position of any funding agency.
\vspace*{\fill}

@@

>>>>

% Title Page
\pagenumbering{roman}

\input{titlepage.tex}

@@

We are grateful to the reviewers for their many useful comments.  We thank
Benjamin Delaware,
Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, and Zhixuan Yang
for valuable discussions and feedback.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the authors and do not necessarily
reflect the position of any funding agency.

@@

\listoffigures

\vspace*{\fill}
\chapterN{List of Abbreviations}

\input{listofabbrev.tex}

% we omit list of symbols first
% \newpage

% \vspace*{\fill}
% \chapterN{List of Symbols}
